% Type of document (article, report, book)
% scrreprt is from koma-script
\documentclass[a4paper, top=2cm, bottom=2cm, left=2.5cm, right=2.5cm, chapterprefix=true, numbers=noenddot]{scrreprt}

%%% PACKAGES %%%
\usepackage[a-1b]{pdfx}  % Add this line for PDF/A-1b compliance
\RedeclareSectionCommand[beforeskip=60pt, afterskip=40pt, font=\fontsize{25}{50}\selectfont\bfseries]{chapter}

% Define chapter and section title format
% add unicode support
\usepackage[utf8]{inputenc}

% Use Helvetica as font
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\usepackage{scrhack}
\usepackage[hyphens]{url}

\usepackage{multirow}

% Better tables
\usepackage{tabularx}

% Better enumerisation env
\usepackage{enumitem}

% Use graphics
\usepackage{graphicx}

% Use date and time
\usepackage{datetime}

% Have subfigures and captions
\usepackage{subcaption}

% Be able to include PDFs in the file
\usepackage{pdfpages}

% Have custom abstract heading
\usepackage{abstract}

% Need a list of equation
\usepackage{tocloft}
% \usepackage{ragged2e}

% Better equation environment
\usepackage{amsmath}

% Symbols for most SI units
\usepackage{siunitx}

\usepackage{csquotes}

% Change page rotation
\usepackage{pdflscape}

% Symbols like checkmark
\usepackage{amssymb}
\usepackage{pifont}

\usepackage[absolute]{textpos}

% Redefine the quote charachter as we are using ngerman
%\GlsSetQuote{+}
% Define the usage of an acronym, Abbreviation (Abbr.), next usage: The Abbr. of ...
%\setacronymstyle{long-short}
% Glossary, hyperref, babel, polyglossia, inputenc, fontenc must be loaded before this package if they are used

%%% Glossary %%%
\usepackage[acronym]{glossaries}

\makeglossaries
%pdflatex main.tex
%makeglossaries main
%pdflatex main.tex
%pdflatex main.tex
\newglossaryentry{iqa}{name={IQA},description={Image Quality Assessment}}
\newglossaryentry{td}{name={TD},description={Teledermatology}}

% Bibliography & citing
\usepackage[
	backend=biber,
	style=apa,
	bibstyle=apa,
	citestyle=apa,
  natbib=true,
	]{biblatex}
\addbibresource{references.bib}

% Clickable Links to Websites and chapters
% From the documentation: "Make sure it comeslastof your loaded packages, to give it a fighting chance of not beingover-written, since its job is to redefine many LATEX commands"
\usepackage{hyperref}
\renewcommand{\chapterautorefname}{Chapter}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Subsection}

%%% COMMAND REBINDINGS %%%
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand{\xmark}{\ding{55}}
\newcommand{\notmark}{\textbf{\textasciitilde}}
% Pro/Con item https://tex.stackexchange.com/questions/145198/change-the-bullet-of-each-item#145203
\newcommand\pro{\item[$+$]}
\newcommand\con{\item[$-$]}

% Define list of equations - Thanks to Charles Clayton: https://tex.stackexchange.com/a/354096
\newcommand{\listequationsname}{\huge{List of Formulas}}
\newlistof{myequations}{equ}{\listequationsname}
\newcommand{\myequations}[1]{
	\addcontentsline{equ}{myequations}{\protect\numberline{\theequation}#1}
}
\setlength{\cftmyequationsnumwidth}{2.3em}
\setlength{\cftmyequationsindent}{1.5em}

% Usage {equation}{caption}{label}
% \indexequation{b = \frac{\pi}{\SI{180}{\degree}}\cdot\beta\cdot 6378.137}{Bogenlänge $b$ des Winkels $\beta$ mit Radius 6378.137m (Distanz zum Erdmittelpunkt am Äquator)}{Bogenlaenge}
\newcommand{\indexequation}[3]{
	\begin{align} \label{#3} \ensuremath{\boxed{#1}} \end{align}
	\myequations{#3} \centering \small \textit{#2} \normalsize \justify }

% Todolist - credit to https://tex.stackexchange.com/questions/247681/how-to-create-checkbox-todo-list
\newlist{todolist}{itemize}{1}
\setlist[todolist]{label=$\square$}

% Nested Enumeratelist credit to https://tex.stackexchange.com/a/54676
\newlist{legal}{enumerate}{10}
\setlist[legal]{label*=\arabic*.}

%%% PATH DEFINITIONS %%%
% Define the path were images are found
\graphicspath{{./img/}{./appendix/}}

%%% GLOSSARY ENTRIES %%%
%\makeglossaries
% \newacronym{RFID}{RFID}{Radio-Frequency Identification}
% \newglossaryentry{HF}{name={HF},description={High Frequency, RFID Tags im Frequenzbereich von 3-30MHz}}

\usepackage{fancyhdr}
\usepackage[top=2.5cm, bottom=2.5cm, left=3.0cm, right=2.5cm]{geometry}

% Clear all header and footer fields
\fancyhf{}

% Header settings
\fancyhead[R]{\leftmark} % Display chapter or section name on the right side of header
\setlength{\headsep}{0.5cm} % Add margin for header text

% Footer settings
\fancyfoot[C]{\thepage\hspace{1.5cm}} % Display page number in the center of footer with added space
\setlength{\footskip}{1.25cm} % Add margin for footer text

% Set the height of the header
\setlength{\headheight}{14.5pt}

% Apply the custom style to the "plain" page style
\fancypagestyle{plain}{%
    \fancyhf{} % Clear all header and footer fields
    \fancyfoot[C]{\thepage\hspace{1.5cm}} % Display page number in the center of footer with added space
    \renewcommand{\headrulewidth}{0pt} % Remove header rule
}

% Apply the custom style to all other page styles
\pagestyle{fancy}

\usepackage{comment}
\usepackage{graphicx}
\usepackage[export]{adjustbox} 
\usepackage{array}
\usepackage{adjustbox}

\newlength{\gridimagewidth}
\setlength{\gridimagewidth}{3cm} % Adjust the width as necessary
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}


%%% TODO Notes %%%
\usepackage{todonotes}

%%% Code %%%
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}

%%% No styling for toc etc. %%%
\addtocontents{toc}{\protect\thispagestyle{empty}}
\addtocontents{lof}{\protect\thispagestyle{empty}}
\addtocontents{lot}{\protect\thispagestyle{empty}}

%%% Tables %%%
\usepackage{booktabs}
\usepackage{caption} % Required for customizing the caption
\usepackage{tablefootnote}
\renewcommand{\thefootnote}{\arabic{footnote}}
\usepackage{url} % For URL formatting

% Customizing the caption to make it bold
\captionsetup{
  labelfont = bf, % Make bold
}
\tolerance=9999
\emergencystretch=10pt
\hyphenpenalty=10000
\exhyphenpenalty=100

%%% Image Placement %%%
\usepackage{floatrow}
\floatsetup[figure]{capposition=bottom}
\floatsetup[table]{capposition=top}
%%% DOCUMENT %%%
\begin{document}

\include{chapters/00_titlepage}

\pagenumbering{Roman}

\chapter*{Abstract}
This research focuses on developing and evaluating automated methods to assess image quality in the context of teledermatology. Teledermatology, a growing field within telemedicine, allows patients to receive dermatological consultations remotely by sending photos of their skin conditions to dermatologists. However, the success of these remote consultations largely depends on the quality of the images provided. Poor-quality images can lead to misdiagnosis or require patients to resend images, causing delays and frustration. This research examines different image quality assessment (IQA) techniques for teledermatology. The goal is to make sure that only good quality images are sent to dermatologists, thereby improving their ability to make accurate medical diagnoses. By implementing these IQA techniques, the aim is to simplify the process, reduce back-and-forth communication, and make teledermatology more efficient and reliable. \par
\vspace{\baselineskip}
\noindent
The methodology involved a detailed review of existing IQA methods, followed by the development of a synthetic distortion pipeline to create a wide range of training datasets from good quality dermatological images. These images were gathered from the Fitzpatrick17k and SCIN datasets. For feature extraction, the state-of-the-art approach called ARNIQA was used, and different machine learning models, including XGBRegressor, XGBClassifier, MLP Regressor, and MLP Classifier, were trained to assess image quality based on seven dermatology quality criteria: lighting, background, field of view, orientation, focus, resolution, and color calibration. The models were trained on synthetic distortions and validated on both synthetically distorted and real-world dermatology images. Performance metrics such as Mean Absolute Error (MAE), R-squared (R\textsuperscript{2}), Spearman’s Rank Order Correlation Coefficient (SRCC), and Cohen’s Kappa were used for evaluation. \par
\vspace{\baselineskip}
\noindent
The results showed that the automated IQA methods can assess image quality in the context of teledermatology, closely matching human evaluations and therefore providing reliable feedback on image quality. The final model achieved good performance across multiple dermatology quality criteria, improving the reliability and effectiveness of teledermatology services. This research highlights the potential of automated IQA systems to improve the accuracy of diagnoses and patient care in remote dermatological consultations. \par

\clearpage

\pagestyle{empty}
\tableofcontents

%\glsaddallunused 
\printglossary[title={List of Abbreviations}] \clearpage

\pagestyle{fancy}

\pagenumbering{arabic}

\include{chapters/01_introduction}

\include{chapters/02_literature}

\include{chapters/03_methodology}

\include{chapters/04_implementation}

\include{chapters/05_results}

%\include{chapters/06_1_discussion}
\include{chapters/06_discussion}

\include{chapters/07_conclusion}

\newpage

\pagenumbering{Roman}

\appendix
% Verhindert das Einfügen von Kapiteltitel kleiner als \chapter
\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

%\printglossary

\listoffigures \clearpage

\listoftables \clearpage

\include{chapters/08_appendix}

%\listofmyequations \pagebreak
\printbibliography

\end{document}
